---
title: "sex_ratio_w1_w2_analysis_6_additional_figs"
author: "Chia-Jung Tsai"
date: "2024-08-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)

library(tidyverse)
library(stringr)
library(RColorBrewer)
library(ggpubr)
library(Hmisc)
library(effsize)
library(stringr)
library(gt)
library(rstatix) #Pairwise t test
library(survey) #Weighted tests

```

> Data is weighted (by Sex and Age_2) and imputed
> Dataset: ATRP_imputed_pswt_v2.csv


```{r}

dt.imp.wt <- readr::read_csv("Data/ATRP_imputed_pswt_v2.csv") # the data set with the bigger sale of weight on AGE (=AGE_2)
dt.imp.wt <- subset(dt.imp.wt, select = -c(...1)) # delete the weird column of "...1" from csv format

```



```{r}
dt.imp.wt$scenario <- factor(dt.imp.wt$equation,
levels = c(1,2,3,4,5,6,7),
labels = c("brown_male_0", "brown_male_50", "brown_male_100", "white_male_100", "German_male_0", "German_male_50", "German_male_100"))

dt.imp.wt$CONT <- factor(dt.imp.wt$CONT,
levels = c(0,1,2,3),
labels = c("Never", " Once", "A few times","Several times"))

dt.imp.wt$REFDE <- factor(dt.imp.wt$REFDE,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt.imp.wt$REFSTA <- factor(dt.imp.wt$REFSTA,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt.imp.wt$REFNHB <- factor(dt.imp.wt$REFNHB,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt.imp.wt$SEXDE <- factor(dt.imp.wt$SEXDE,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt.imp.wt$SEXSTA <- factor(dt.imp.wt$SEXSTA,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt.imp.wt$SEXNHB <- factor(dt.imp.wt$SEXNHB,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt.imp.wt$AGE <- factor(dt.imp.wt$AGE,
levels = c(1,2,3,4,5,6,7,8,9,10),
labels = c("18-24", "25-29", "30-34","35-39","40-44","45-49","50-54","55-59","60-64","Over65"))


dt.imp.wt$AGE_2 <- factor(dt.imp.wt$AGE_2,
levels = c(1,2,3,4,5),
labels = c("18-29", "30-39","40-49","50-59","60-64"))


dt.imp.wt$SEX <- factor(dt.imp.wt$SEX,
levels = c(0,1,2),
labels = c("Male", "Female", "Diverse"))

dt.imp.wt$origin<- ifelse(dt.imp.wt$CTR=="DE","Germany","Not Germany") 

dt.imp.wt$DE <- factor(dt.imp.wt$DE,
levels = c(0,1),
labels = c("Not In Germany", "Germany"))

dt.imp.wt$BUNDESLAND <- factor(dt.imp.wt$BUNDESLAND,
levels = c("BW","BY","BE","BB","HB","HH","HE","NI",
           "MV","NW","RP","SL","SN","ST","SH","TH"),
labels = c("Baden-Württemberg",
           "Bayern",
           "Berlin",
           "Brandenburg",
           "Bremen",
           "Hamburg",
           "Hessen", 
           "Niedersachsen", 
           "Mecklenburg-Vorpommern", 
           "Nordrhein-Westfalen", 
           "Rheinland-Pfalz", 
           "Saarland", 
           "Sachsen", 
           "Sachsen-Anhalt", 
           "Schleswig-Holstein", 
           "Thüringen"))

dt.imp.wt$BER <- factor(dt.imp.wt$BER,
levels = c(1,2,3,4,5,6,7,8,9,10,11,12),
labels = c("Mitte",
           "Friedrichshain-Kreuzberg", 
           "Neukölln", 
           "Charlottenburg-Wilmersdorf", 
           "Spandau", 
           "Steglitz-Zehlendorf", 
           "Tempelhof-Schöneberg", 
           "Reinickendorf", 
           "Pankow", 
           "Marzahn-Hellersdorf", 
           "Lichtenberg", 
           "Treptow-Köpenick"))

dt.imp.wt$JOBSTATUS <- factor(dt.imp.wt$JOBSTATUS,
 levels = c(1,2,3,4,5,6,7,8),
 labels = c("Paid work", 
            "School/training",
            "Unemployed and actively looking for a job",
            "Unemployed, wanting a job but not actively looking",
            "Chronically ill or disabled",
            "Pre-retired/retired/early retired/retired",
            "Voluntary military service/federal voluntary service/FSJ/FÖJ",
            "Housework, caring for children or other people"))

dt.imp.wt$EDU <- factor(dt.imp.wt$EDU,
 levels = c(1,2,3,4,5),
 labels = c("No formal education",
            "Elementary school",
            "Further school/secondary school",
            "University education (e.g. Bachelor, Master)",
            "Graduate studies (e.g. doctorate, medical doctorate"))

dt.imp.wt$PRTALSTATUS <- factor(dt.imp.wt$PRTALSTATUS,
 levels = c(1,2,3),
 labels = c("Yes",
            "No",
            "Not applicable"))

dt.imp.wt$PLT <- factor(dt.imp.wt$PLT,
levels = c(1,2,3,4,5,6,7,8,9,10),
labels = c("CDU/CSU",
           "SPD", 
           "Buendnis 90/Gruene", 
           "Die Linke", 
           "FDP",
           "NPD/Republikaner/Die Rechte", 
           "AfD",
           "Others", 
           "Did not vote", 
           "Not qualified to vote"))


```


```{r}

# recode PLT into AfD/non-AfD;recode age into 50/over 50

dt.imp.wt <- dt.imp.wt %>%
  mutate(AfD=case_when(
    PLT=="AfD" ~ "AfD",
    PLT=="Did not vote"|PLT=="Not qualified to vote" ~ "Not Vote or Not Qualified" ,
    .default = "Non-AfD",
  ))


dt.imp.wt <- dt.imp.wt %>%
  mutate(AGE_50=case_when(
    AGE_2=="18-29"|AGE_2=="30-39"|AGE_2=="40-49" ~ "18-49",
    AGE_2=="50-59"|AGE_2=="60-64" ~ "50-64" ,
  ))

```



### reverse codeing for outcomes (1: postive; 6: negative)

> R "ATTITUDES" --> Non-Acceptance (1:Acceptance; 6:Non-Acceptance)
> R "PCPJOBNHB" (1: Threats to job competition ;6: No Threats to job competition ) --> Threat to Job Competition (1: No Threat; 6: Threats)
> "PCPMATENHB" (1: No Threats to mate competition ;6: Threats to mate competition ) 
> R "PCPCULNHB" (1: Threats to Culture ;6: Threats to culture) --> Threat to Culture (1: No Threat; 6: Threats)
> R "PCPSAFENHB" (1: Not Safe ;6: Safe) --> Safety (1: No Safety concern; 6 High Safety concern)


```{r, echo=FALSE}
# only 4 of 5 outcomes reversed 
dt.imp.wt <-dt.imp.wt%>%
  mutate_at(c("ATTITUDES", "PCPJOBNHB", "PCPCULNHB","PCPSAFENHB"), 
            .funs = list(
              ~case_when( 
                .==1 ~ 5,
                .==2 ~ 4,
                .==3 ~ 3,
                .==4 ~ 2,
                .==5 ~ 1,
                .==6 ~ 0
                )
              ))

```



```{r, echo=FALSE}
# not reversed 
dt.imp.wt <-dt.imp.wt%>%
  mutate_at("PCPMATENHB", 
            .funs = list(
              ~case_when( 
                .==1 ~ 0,
                .==2 ~ 1,
                .==3 ~ 2,
                .==4 ~ 3,
                .==5 ~ 4,
                .==6 ~ 5
                )
              ))

```



```{r}
# rename outcomes
dt.imp.wt<-dt.imp.wt %>% 
  rename ("non_accept"="ATTITUDES",
          "threat_job"="PCPJOBNHB", 
          "threat_mate"="PCPMATENHB", 
          "threat_culture"="PCPCULNHB",
          "threat_safety"="PCPSAFENHB")


```


```{r, fig.width=10, fig.height=4}

ggplot(dt.imp.wt, aes(scenario, non_accept, color=SEX)) + geom_violin() 

```



```{r}

model0 = summary(lm(non_accept ~ factor(scenario), weights = psweight, data = dt.imp.wt)); model0

```



```{r}
model1 = summary(lm(non_accept ~ factor(scenario)+SEX, weights = psweight, data = dt.imp.wt)); model1

```

```{r}

model2 = summary(lm(non_accept ~ factor(scenario)+SEX+factor(scenario):SEX, weights = psweight, data = dt.imp.wt)); model2

```

```{r}

model3 = lm(non_accept ~ I(scenario =='brown_male_100') + I(SEX == 'Male'), weights = psweight, data = dt.imp.wt); model3

```

```{r}
#  expected salary for female, all other scenarios  = B0 = 2.4110 
# expected salary for female 100_non-white_male holding B2 constant =
  # B0 + B1 = 2.4110 + 1.4546 = 3.8656
# expected salary for male all other scenarios holding B1 constant = 
  # B0 + B2 = 2.4110 + 0.2958 = 2.7068
# expected salary for male 100_non-white_male = 
  # B0 + B1 + B2 = 2.4110 + 1.4546 + 0.2958 = 4.1614

```

```{r}
pred.val.sex.scen = matrix(c(2.4110, 3.8656, 2.7068, 4.1614), ncol=2, byrow=TRUE)
colnames(pred.val.sex.scen) = c("all_others", "100_non_white_male")
rownames(pred.val.sex.scen) = c("female", "male")
pred.val.sex.scen = as.table(pred.val.sex.scen)

barplot(pred.val.sex.scen, main="Predicted values of non-acceptance by sex and scenario",
         col=c("lightpink","lightblue"),    legend = rownames(pred.val.sex.scen), 
        beside=TRUE)

```

```{r}

Model.int = lm(non_accept ~ I(scenario == 'brown_male_100') + SEX + I(scenario == 'brown_male_100')*SEX, weights = psweight, data=dt.imp.wt)
summary(Model.int)

```

```{r}

Model.coef =  coefficients(Model.int)

```


```{r}
#B0 is the expected mean for other_scen females
Model.coef[1]+(Model.coef[2]*0)

# simple intercept = (b0 + b2) = average non_accept for males who are other_scen (b1=0)
Model.coef[1] + Model.coef[3]

# simple slope = (B1 + B3) captures the effect of 100_non_white_male for males
Model.coef[2] + Model.coef[3]

# B3 captures the difference in effect for 100_non_white_male among men & women
Model.coef[4]


```


```{r}
# interaction was not sig so not different from 0

# E(Y|b1=1, b2=1 ) (B0 + B2) + (B1 + B3)*1 
# effects of being male on salary given rank
scen.wit.sex = (Model.coef[1] + Model.coef[3]) + 
  ((Model.coef[2] + Model.coef[4])*1); scen.wit.sex

```



```{r}

#  expected salary for female, all other scenarios  = B0 = 2.7198 
# expected salary for female 100_non-white_male holding B2 constant =
  # B0 + B1 = 2.7198 + 1.3543 = 4.0741
# expected salary for male all other scenarios holding B1 constant = 
  # B0 + B2 = 2.7198 + 0.2148 = 2.9346
# expected salary for male 100_non-white_male = 
  # B0 + B1 + B2 = 2.7198 + 1.3543 +0.2148 = 4.2889


pred.val.sex.scen = matrix(c(2.7198, 4.0741, 2.9346, 4.2889), ncol=2, byrow=TRUE)
colnames(pred.val.sex.scen) = c("all_others", "100_non_white_male")
rownames(pred.val.sex.scen) = c("female", "male")
pred.val.sex.scen = as.table(pred.val.sex.scen)

barplot(pred.val.sex.scen, 
        main="Predicted values of salary by sex and rank w/ interaction",
        col=c("lightpink","lightblue"), 
        legend = rownames(pred.val.sex.scen), beside=TRUE)

```

Paired groups


```{r}

dt_1 <- dt.imp.wt %>% filter(scenario=="brown_male_0"|scenario=="brown_male_50")
dt_2 <- dt.imp.wt %>% filter(scenario=="brown_male_50"|scenario=="brown_male_100")
dt_3 <- dt.imp.wt %>% filter(scenario=="brown_male_100"|scenario=="white_male_100")
dt_4 <- dt.imp.wt %>% filter(scenario=="German_male_0"|scenario=="German_male_50")
dt_5 <- dt.imp.wt %>% filter(scenario=="German_male_50"|scenario=="German_male_100")


```



```{r}

Bm050  = summary(lm(non_accept ~ scenario ,weights = psweight, data = dt_1)); Bm050
Bm50100  = summary(lm(non_accept ~ scenario, weights = psweight, data = dt_2));Bm50100
BmWm100  = summary(lm(non_accept ~ scenario, weights = psweight, data = dt_3));BmWm100
Gm050  = summary(lm(non_accept ~ scenario, weights = psweight, data = dt_4));Gm050
Gm50100  = summary(lm(non_accept ~ scenario, weights = psweight, data = dt_5));Gm50100

```



```{r}

Bm050.int  = summary(lm(non_accept ~ I(scenario =='brown_male_0')*SEX ,weights = psweight, data = dt_1)); Bm050.int
Bm50100.int  = summary(lm(non_accept ~ I(scenario =='brown_male_50')*SEX, weights = psweight, data = dt_2));Bm50100.int
BmWm100.int  = summary(lm(non_accept ~ I(scenario =='brown_male_100')*SEX, weights = psweight, data = dt_3));BmWm100.int
Gm050.int  = summary(lm(non_accept ~ I(scenario =='German_male_0')*SEX, weights = psweight, data = dt_4));Gm050.int
Gm50100.int  = summary(lm(non_accept ~ I(scenario =='German_male_50')*SEX, weights = psweight, data = dt_5));Gm50100.int


```



```{r}

Bm050.int  = summary(lm(non_accept ~ I(scenario =='brown_male_0'):SEX ,weights = psweight, data = dt_1)); Bm050.int
Bm50100.int  = summary(lm(non_accept ~ I(scenario =='brown_male_50'):SEX, weights = psweight, data = dt_2));Bm50100.int
BmWm100.int  = summary(lm(non_accept ~ I(scenario =='brown_male_100'):SEX, weights = psweight, data = dt_3));BmWm100.int
Gm050.int  = summary(lm(non_accept ~ I(scenario =='German_male_0'):SEX, weights = psweight, data = dt_4));Gm050.int
Gm50100.int  = summary(lm(non_accept ~ I(scenario =='German_male_50'):SEX, weights = psweight, data = dt_5));Gm50100.int


```



```{r}

# library(modelsummary)
# library(gt)

# build table with `modelsummary` 

cm <- c('(Intercept)' = '(Intercept)',
        'I(scenario == "brown_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_100")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_100")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_100")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants')
          
         
cap <- 'Non Acceptance across the Change of Conditions and Gender of Respondants'


models <- list(Bm050.int, Bm50100.int, BmWm100.int, Gm050.int, Gm50100.int)
tab_1 <- modelsummary(models,  
                output = "gt",
                coef_map = cm, stars = TRUE, 
                title = cap, gof_omit = 'IC|Log|Adj') 




# customize table with `gt`

gt_ob<-tab_1 %>%

    # column labels
    tab_spanner(label = 'Non-white refugee male 0% and 50%', columns = 2) %>%
    tab_spanner(label = 'Non-white refugee male 50% and 100%', columns = 3) %>%
    tab_spanner(label = 'Non-white male 100% and white refugee male 100%', columns = 4) %>%
    tab_spanner(label = 'German male\n0% and 50%', columns = 5) %>%
    tab_spanner(label = 'German male 50% and 100%', columns = 6) %>%

    # footnote
    tab_footnote(footnote = md("Reference: Female Respndants"),
                 locations = cells_body(rows = 3, columns = 1)) %>%
    
    # text and background color
    tab_style(style = cell_text(color = 'red'),
              locations = cells_body(rows = 3)) %>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 5))%>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 7)) %>%
    
  # increase the width of each column
    cols_width(everything() ~ px(160))%>% 
  # increase the height of each row
    tab_options(data_row.padding = px(3))

```

```{r}

gtsave(gt_ob, "U:/sex_ratio/output/tab_S16.png", expand = 10)

```



```{r}

Bm050.int.j  = summary(lm(threat_job ~ I(scenario =='brown_male_0'):SEX ,weights = psweight, data = dt_1)); Bm050.int.j
Bm50100.int.j  = summary(lm(threat_job ~ I(scenario =='brown_male_50'):SEX, weights = psweight, data = dt_2));Bm50100.int.j
BmWm100.int.j  = summary(lm(threat_job ~ I(scenario =='brown_male_100'):SEX, weights = psweight, data = dt_3));BmWm100.int.j
Gm050.int.j  = summary(lm(threat_job ~ I(scenario =='German_male_0'):SEX, weights = psweight, data = dt_4));Gm050.int.j
Gm50100.int.j  = summary(lm(threat_job ~ I(scenario =='German_male_50'):SEX, weights = psweight, data = dt_5));Gm50100.int.j


```



```{r}

# library(modelsummary)
# library(gt)

# build table with `modelsummary` 

cm <- c('(Intercept)' = '(Intercept)',
        'I(scenario == "brown_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_100")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_100")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_100")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants')
          
         
cap <- 'Percieved Threats to Job Competition across the Change of Conditions and Gender of Respondants'


models_2 <- list(Bm050.int.j, Bm50100.int.j, BmWm100.int.j, Gm050.int.j, Gm50100.int.j)
tab_2 <- modelsummary(models_2,  
                output = "gt",
                coef_map = cm, stars = TRUE, 
                title = cap, gof_omit = 'IC|Log|Adj') 




# customize table with `gt`

gt_ob_2<-tab_2 %>%

    # column labels
    tab_spanner(label = 'Non-white refugee male 0% and 50%', columns = 2) %>%
    tab_spanner(label = 'Non-white refugee male 50% and 100%', columns = 3) %>%
    tab_spanner(label = 'Non-white male 100% and white refugee male 100%', columns = 4) %>%
    tab_spanner(label = 'German male\n0% and 50%', columns = 5) %>%
    tab_spanner(label = 'German male 50% and 100%', columns = 6) %>%

    # footnote
    tab_footnote(footnote = md("Reference: Female Respndants"),
                 locations = cells_body(rows = 3, columns = 1)) %>%
    
    # text and background color
    tab_style(style = cell_text(color = 'red'),
              locations = cells_body(rows = 3)) %>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 5))%>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 7)) %>%
    
  # increase the width of each column
    cols_width(everything() ~ px(160))%>% 
  # increase the height of each row
    tab_options(data_row.padding = px(3))

```

```{r}

gtsave(gt_ob_2, "U:/sex_ratio/output/tab_S17.png", expand = 10)

```



```{r}

Bm050.int.m = summary(lm(threat_mate ~ I(scenario =='brown_male_0'):SEX ,weights = psweight, data = dt_1)); Bm050.int.m
Bm50100.int.m = summary(lm(threat_mate ~ I(scenario =='brown_male_50'):SEX, weights = psweight, data = dt_2));Bm50100.int.m
BmWm100.int.m = summary(lm(threat_mate ~ I(scenario =='brown_male_100'):SEX, weights = psweight, data = dt_3));BmWm100.int.m
Gm050.int.m = summary(lm(threat_mate ~ I(scenario =='German_male_0'):SEX, weights = psweight, data = dt_4));Gm050.int.m
Gm50100.int.m = summary(lm(threat_mate ~ I(scenario =='German_male_50'):SEX, weights = psweight, data = dt_5));Gm50100.int.m


```



```{r}

# library(modelsummary)
# library(gt)

# build table with `modelsummary` 

cm <- c('(Intercept)' = '(Intercept)',
        'I(scenario == "brown_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_100")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_100")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_100")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants')
          
         
cap <- 'Percieved Threats to Mate Competition across the Change of Conditions and Gender of Respondants'


models_3 <- list(Bm050.int.m, Bm50100.int.m, BmWm100.int.m, Gm050.int.m, Gm50100.int.m)
tab_3 <- modelsummary(models_3,  
                output = "gt",
                coef_map = cm, stars = TRUE, 
                title = cap, gof_omit = 'IC|Log|Adj') 




# customize table with `gt`

gt_ob_3 <-tab_3 %>%

    # column labels
    tab_spanner(label = 'Non-white refugee male 0% and 50%', columns = 2) %>%
    tab_spanner(label = 'Non-white refugee male 50% and 100%', columns = 3) %>%
    tab_spanner(label = 'Non-white male 100% and white refugee male 100%', columns = 4) %>%
    tab_spanner(label = 'German male\n0% and 50%', columns = 5) %>%
    tab_spanner(label = 'German male 50% and 100%', columns = 6) %>%

    # footnote
    tab_footnote(footnote = md("Reference: Female Respndants"),
                 locations = cells_body(rows = 3, columns = 1)) %>%
    
    # text and background color
    tab_style(style = cell_text(color = 'red'),
              locations = cells_body(rows = 3)) %>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 5))%>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 7)) %>%
    
  # increase the width of each column
    cols_width(everything() ~ px(160))%>% 
  # increase the height of each row
    tab_options(data_row.padding = px(3))

```

```{r}

gtsave(gt_ob_3, "U:/sex_ratio/output/tab_S18.png", expand = 10)

```




```{r}

Bm050.int.s = summary(lm(threat_safety ~ I(scenario =='brown_male_0'):SEX ,weights = psweight, data = dt_1)); Bm050.int.s
Bm50100.int.s = summary(lm(threat_safety ~ I(scenario =='brown_male_50'):SEX, weights = psweight, data = dt_2));Bm50100.int.s
BmWm100.int.s = summary(lm(threat_safety ~ I(scenario =='brown_male_100'):SEX, weights = psweight, data = dt_3));BmWm100.int.s
Gm050.int.s = summary(lm(threat_safety ~ I(scenario =='German_male_0'):SEX, weights = psweight, data = dt_4));Gm050.int.s
Gm50100.int.s = summary(lm(threat_safety ~ I(scenario =='German_male_50'):SEX, weights = psweight, data = dt_5));Gm50100.int.s


```



```{r}

# library(modelsummary)
# library(gt)

# build table with `modelsummary` 

cm <- c('(Intercept)' = '(Intercept)',
        'I(scenario == "brown_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_100")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_100")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_100")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants')
          
         
cap <- 'Percieved Threats to Safety across the Change of Conditions and Gender of Respondants'


models_4 <- list(Bm050.int.s, Bm50100.int.s, BmWm100.int.s, Gm050.int.s, Gm50100.int.s)
tab_4 <- modelsummary(models_4,  
                output = "gt",
                coef_map = cm, stars = TRUE, 
                title = cap, gof_omit = 'IC|Log|Adj') 




# customize table with `gt`

gt_ob_4 <-tab_4 %>%

    # column labels
    tab_spanner(label = 'Non-white refugee male 0% and 50%', columns = 2) %>%
    tab_spanner(label = 'Non-white refugee male 50% and 100%', columns = 3) %>%
    tab_spanner(label = 'Non-white male 100% and white refugee male 100%', columns = 4) %>%
    tab_spanner(label = 'German male\n0% and 50%', columns = 5) %>%
    tab_spanner(label = 'German male 50% and 100%', columns = 6) %>%

    # footnote
    tab_footnote(footnote = md("Reference: Female Respndants"),
                 locations = cells_body(rows = 3, columns = 1)) %>%
    
    # text and background color
    tab_style(style = cell_text(color = 'red'),
              locations = cells_body(rows = 3)) %>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 5))%>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 7)) %>%
    
  # increase the width of each column
    cols_width(everything() ~ px(160))%>% 
  # increase the height of each row
    tab_options(data_row.padding = px(3))

```

```{r}

gtsave(gt_ob_4, "U:/sex_ratio/output/tab_S20.png", expand = 10)

```



```{r}
Bm050.int.c = summary(lm(threat_culture ~ I(scenario =='brown_male_0'):SEX ,weights = psweight, data = dt_1)); Bm050.int.c
Bm50100.int.c = summary(lm(threat_culture ~ I(scenario =='brown_male_50'):SEX, weights = psweight, data = dt_2));Bm50100.int.c
BmWm100.int.c = summary(lm(threat_culture ~ I(scenario =='brown_male_100'):SEX, weights = psweight, data = dt_3));BmWm100.int.c

```



```{r}

# library(modelsummary)
# library(gt)

# build table with `modelsummary` 

cm <- c('(Intercept)' = '(Intercept)',
        'I(scenario == "brown_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "brown_male_100")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "brown_male_100")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "brown_male_100")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_0")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_0")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_0")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants',
        'I(scenario == "German_male_50")TRUE:SEXMale'= 'Effect of Male Respndants (Within the Same Condition)',
        'I(scenario == "German_male_50")FALSE:SEXFemale'= 'Effect of Condition Changes (within Female Respondants)',
        'I(scenario == "German_male_50")FALSE:SEXMale'='Interation of Condition Changes and Male Respndants')
          
         
cap <- 'Percieved Threats to German Culture across the Change of Conditions and Gender of Respondants'


models_5 <- list(Bm050.int.c, Bm50100.int.c, BmWm100.int.c)
tab_5 <- modelsummary(models_5,  
                output = "gt",
                coef_map = cm, stars = TRUE, 
                title = cap, gof_omit = 'IC|Log|Adj') 




# customize table with `gt`

gt_ob_5 <-tab_5 %>%

    # column labels
    tab_spanner(label = 'Non-white refugee male 0% and 50%', columns = 2) %>%
    tab_spanner(label = 'Non-white refugee male 50% and 100%', columns = 3) %>%
    tab_spanner(label = 'Non-white male 100% and white refugee male 100%', columns = 4) %>%

    # footnote
    tab_footnote(footnote = md("Reference: Female Respndants"),
                 locations = cells_body(rows = 3, columns = 1)) %>%
    
    # text and background color
    tab_style(style = cell_text(color = 'red'),
              locations = cells_body(rows = 3)) %>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 5))%>%
    tab_style(style = cell_fill(color = 'lightblue'),
              locations = cells_body(rows = 7)) %>%
    
  # increase the width of each column
    cols_width(everything() ~ px(160))%>% 
  # increase the height of each row
    tab_options(data_row.padding = px(3))

```

```{r}

gtsave(gt_ob_5, "U:/sex_ratio/output/tab_S19.png", expand = 10)

```























