---
title: "sex_ratio_w1_w2_analysis_supplementary_material_D"
author: "Chia-Jung Tsai"
date: "2024-05-10"
output: html_document
---
---
title: "sex_ratio_w1_w2_analysis_supplementary_material_C"
author: "Chia-Jung Tsai"
date: "2023-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(stringr)
library(RColorBrewer)
library(ggpubr)
library(Hmisc)
library(effsize)
library(stringr)
library(gt)
library(data.table)
library(rstatix) #Pairwise t test
library(survey) #Weighted tests

```

```{r, echo=FALSE, message=FALSE, results='hide', cache=TRUE}

dt_for_sm <- readr::read_csv("Data/ATRP_imputed_pswt_v2.csv") # the data set with the bigger sale of weight on AGE (=AGE_2)
dt_for_sm <- subset(dt_for_sm, select = -c(...1)) # delete the weird column of "...1" from csv format

```

```{r}
dt_for_sm$scenario <- factor(dt_for_sm$equation,
levels = c(1,2,3,4,5,6,7),
labels = c("brown_male_0", "brown_male_50", "brown_male_100", "white_male_100", "German_male_0", "German_male_50", "German_male_100"))

dt_for_sm$CONT <- factor(dt_for_sm$CONT,
levels = c(0,1,2,3),
labels = c("Never", " Once", "A few times","Several times"))

dt_for_sm$REFDE <- factor(dt_for_sm$REFDE,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt_for_sm$REFSTA <- factor(dt_for_sm$REFSTA,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt_for_sm$REFNHB <- factor(dt_for_sm$REFNHB,
levels = c(1,2,3,4),
labels = c("lower than 1%", "1.5%", "3%","higher than 5%"))

dt_for_sm$SEXDE <- factor(dt_for_sm$SEXDE,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt_for_sm$SEXSTA <- factor(dt_for_sm$SEXSTA,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt_for_sm$SEXNHB <- factor(dt_for_sm$SEXNHB,
levels = c(1,2,3,4,5),
labels = c("women>>men", "women>men", "women=men","women<men","women<<men"))

dt_for_sm$AGE <- factor(dt_for_sm$AGE,
levels = c(1,2,3,4,5,6,7,8,9,10),
labels = c("18-24", "25-29", "30-34","35-39","40-44","45-49","50-54","55-59","60-64","Over65"))


dt_for_sm$AGE_2 <- factor(dt_for_sm$AGE_2,
levels = c(1,2,3,4,5),
labels = c("18-29", "30-39","40-49","50-59","60-64"))


dt_for_sm$SEX <- factor(dt_for_sm$SEX,
levels = c(0,1,2),
labels = c("Male", "Female", "Diverse"))

dt_for_sm$origin<- ifelse(dt_for_sm$CTR=="DE","Germany","Not Germany") 

dt_for_sm$DE <- factor(dt_for_sm$DE,
levels = c(0,1),
labels = c("Not In Germany", "Germany"))

dt_for_sm$BUNDESLAND <- factor(dt_for_sm$BUNDESLAND,
levels = c("BW","BY","BE","BB","HB","HH","HE","NI",
           "MV","NW","RP","SL","SN","ST","SH","TH"),
labels = c("Baden-Württemberg",
           "Bayern",
           "Berlin",
           "Brandenburg",
           "Bremen",
           "Hamburg",
           "Hessen", 
           "Niedersachsen", 
           "Mecklenburg-Vorpommern", 
           "Nordrhein-Westfalen", 
           "Rheinland-Pfalz", 
           "Saarland", 
           "Sachsen", 
           "Sachsen-Anhalt", 
           "Schleswig-Holstein", 
           "Thüringen"))

dt_for_sm$BER <- factor(dt_for_sm$BER,
levels = c(1,2,3,4,5,6,7,8,9,10,11,12),
labels = c("Mitte",
           "Friedrichshain-Kreuzberg", 
           "Neukölln", 
           "Charlottenburg-Wilmersdorf", 
           "Spandau", 
           "Steglitz-Zehlendorf", 
           "Tempelhof-Schöneberg", 
           "Reinickendorf", 
           "Pankow", 
           "Marzahn-Hellersdorf", 
           "Lichtenberg", 
           "Treptow-Köpenick"))

dt_for_sm$JOBSTATUS <- factor(dt_for_sm$JOBSTATUS,
 levels = c(1,2,3,4,5,6,7,8),
 labels = c("Paid work", 
            "School/training",
            "Unemployed and actively looking for a job",
            "Unemployed, wanting a job but not actively looking",
            "Chronically ill or disabled",
            "Pre-retired/retired/early retired/retired",
            "Voluntary military service/federal voluntary service/FSJ/FÖJ",
            "Housework, caring for children or other people"))

dt_for_sm$EDU <- factor(dt_for_sm$EDU,
 levels = c(1,2,3,4,5),
 labels = c("No formal education",
            "Elementary school",
            "Further school/secondary school",
            "University education (e.g. Bachelor, Master)",
            "Graduate studies (e.g. doctorate, medical doctorate"))

dt_for_sm$PRTALSTATUS <- factor(dt_for_sm$PRTALSTATUS,
 levels = c(1,2,3),
 labels = c("Yes",
            "No",
            "Not applicable"))

dt_for_sm$PLT <- factor(dt_for_sm$PLT,
levels = c(1,2,3,4,5,6,7,8,9,10),
labels = c("CDU/CSU",
           "SPD", 
           "Buendnis 90/Gruene", 
           "Die Linke", 
           "FDP",
           "NPD/Republikaner/Die Rechte", 
           "AfD",
           "Others", 
           "Did not vote", 
           "Not qualified to vote"))


```

```{r}

# recode PLT into AfD/non-AfD;recode age into 50/over 50

dt_for_sm <- dt_for_sm %>%
  mutate(AfD=case_when(
    PLT=="AfD" ~ "AfD",
    PLT=="Did not vote"|PLT=="Not qualified to vote" ~ "Not Vote or Not Qualified" ,
    .default = "Non-AfD",
  ))


dt_for_sm <- dt_for_sm %>%
  mutate(AGE_50=case_when(
    AGE_2=="18-29"|AGE_2=="30-39"|AGE_2=="40-49" ~ "18-49",
    AGE_2=="50-59"|AGE_2=="60-64" ~ "50-64" ,
  ))

```

```{r, echo=FALSE}
# only 4 of 5 outcomes reversed 
dt_for_sm <-dt_for_sm%>%
  mutate_at(c("ATTITUDES", "PCPJOBNHB", "PCPCULNHB","PCPSAFENHB"), 
            .funs = list(
              ~case_when( 
                .==1 ~ 5,
                .==2 ~ 4,
                .==3 ~ 3,
                .==4 ~ 2,
                .==5 ~ 1,
                .==6 ~ 0
                )
              ))

```

```{r, echo=FALSE}
# not reversed 
dt_for_sm <-dt_for_sm%>%
  mutate_at("PCPMATENHB", 
            .funs = list(
              ~case_when( 
                .==1 ~ 0,
                .==2 ~ 1,
                .==3 ~ 2,
                .==4 ~ 3,
                .==5 ~ 4,
                .==6 ~ 5
                )
              ))

```

```{r}
# rename outcomes
dt_for_sm<-dt_for_sm %>% 
  rename ("non_accept"="ATTITUDES",
          "threat_job"="PCPJOBNHB", 
          "threat_mate"="PCPMATENHB", 
          "threat_culture"="PCPCULNHB",
          "threat_safety"="PCPSAFENHB")


```


### The interplay with scenarios and gender
#### All groups 

```{r}
Non_accept_sex <- dt_for_sm %>% 
  group_by(scenario, SEX)%>%
  summarise(mean=weighted.mean(non_accept, psweight),
            sd=sqrt(wtd.var(non_accept, psweight)),
            se= sd/sqrt(length(.)),
            ci=1.96*se) %>% 
  mutate(Threat_type="Non-Acceptance")

Job_com_sex <- dt_for_sm %>% 
  group_by(scenario, SEX)%>%
  summarise(mean=weighted.mean(threat_job, psweight),
            sd=sqrt(wtd.var(threat_job, psweight)),
            se= sd/sqrt(length(.)),
            ci=1.96*se) %>% 
  mutate(Threat_type="Threats to Job Competition")


Mate_com_sex <- dt_for_sm %>% 
  group_by(scenario, SEX)%>%
  summarise(mean=weighted.mean(threat_mate, psweight),
            sd=sqrt(wtd.var(threat_mate, psweight)),
            se= sd/sqrt(length(.)),
            ci=1.96*se) %>% 
  mutate(Threat_type="Threats to Mate Competition")


Cul_thr_sex <- dt_for_sm %>% 
  group_by(scenario, SEX)%>%
  summarise(mean=weighted.mean(threat_culture, psweight),
            sd=sqrt(wtd.var(threat_culture, psweight)),
            se= sd/sqrt(length(.)),
            ci=1.96*se) %>% 
  mutate(Threat_type="Threats to German Culture")


Safe_con_sex <- dt_for_sm %>% 
  group_by(scenario, SEX)%>%
  summarise(mean=weighted.mean(threat_safety, psweight),
            sd=sqrt(wtd.var(threat_safety, psweight)),
            se= sd/sqrt(length(.)),
            ci=1.96*se) %>% 
  mutate(Threat_type="Threats to Safety")


Thr_sex <- rbind(Non_accept_sex, Job_com_sex, Mate_com_sex, Cul_thr_sex, Safe_con_sex)


```


### Non-Acceptance
##### Unweighted pairwise p value
```{r}

non_accept_sex_t_test <-dt_for_sm %>% group_by(SEX)%>%
  pairwise_t_test(non_accept~scenario, pool.sd = FALSE)%>% 
  mutate(significance = case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

non_accept_sex_t_test <- non_accept_sex_t_test %>% add_xy_position(x="scenario", dodge=0.9)
non_accept_sex_t_test <- non_accept_sex_t_test %>% 
  filter(xmin==1&xmax==2&SEX=="Male"|xmin==1&xmax==2&SEX=="Female"|xmin==2&xmax==3&SEX=="Male"|xmin==2&xmax==3&SEX=="Female"|
           xmin==1&xmax==3&SEX=="Male"|xmin==1&xmax==3&SEX=="Female"|xmin==3&xmax==4&SEX=="Male"|xmin==3&xmax==4&SEX=="Female"|
           xmin==1&xmax==5&SEX=="Male"|xmin==1&xmax==5&SEX=="Female"|xmin==2&xmax==6&SEX=="Male"|xmin==2&xmax==6&SEX=="Female"|
           xmin==3&xmax==7&SEX=="Male"|xmin==3&xmax==7&SEX=="Female")

```



###### Weighted p value, combined into unweighted dataframe

```{r}
# data split into  male and female

data_male <-dt_for_sm %>% filter(SEX=="Male")
data_female <-dt_for_sm %>% filter(SEX=="Female")


# Function of weighted t-test for a pair of scenarios
perform_weighted_t_test <- function(data, scenario1, scenario2, psweight) {
  filtered_data <- data %>%
    filter(scenario %in% c(scenario1, scenario2))
  survey_design <- svydesign(ids = ~1, weights = psweight, data = filtered_data)
  weighted_t_test_result <- svyttest(non_accept ~ scenario, design = survey_design)
  return(weighted_t_test_result$p.value)
}

# Paired scenarios
scenario_pairs <- list(
  c("brown_male_0", "brown_male_50"),
  c("brown_male_0", "brown_male_100"),
  c("brown_male_0", "German_male_0"),
  c("brown_male_50", "brown_male_100"),
  c("brown_male_50", "German_male_50"),
  c("brown_male_100", "white_male_100"),
  c("brown_male_100", "German_male_100")
)

# Perform weighted t-test for each pair of scenarios
p_weighted_male <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_male, pair[1], pair[2], ~psweight)
})

p_weighted_male<- as.data.frame(p_weighted_male)

p_weighted_female <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_female, pair[1], pair[2], ~psweight)
})

p_weighted_female<- as.data.frame(p_weighted_female)
colnames(p_weighted_male)= colnames(p_weighted_female)
p_weighted <- bind_rows(p_weighted_male, p_weighted_female)

colnames(p_weighted) <- "p_weighted"

# Combine results
non_accept_sex_t_test <- cbind(non_accept_sex_t_test, p_weighted)

# Remove objects
rm(scenario_pairs, p_weighted_male, p_weighted_female, p_weighted)


non_accept_sex_t_test <- non_accept_sex_t_test %>% 
  mutate(signif_weighted = case_when(
    p_weighted < 0.001 ~ "***",
    p_weighted < 0.01 ~ "**",
    p_weighted < 0.05 ~ "*",
    p_weighted < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

```



```{r}

# Recode the values based on the SEX variable
non_accept_sex_t_test$xmin <- ifelse(non_accept_sex_t_test$SEX == "Male", non_accept_sex_t_test$xmin - 0.25, non_accept_sex_t_test$xmin + 0.25)
non_accept_sex_t_test$xmax <- ifelse(non_accept_sex_t_test$SEX == "Male", non_accept_sex_t_test$xmax - 0.25, non_accept_sex_t_test$xmax + 0.25)

```


```{r}

plot_non_accept_sex <- Non_accept_sex  %>% 
  ggplot()+
  geom_bar(aes(x=scenario, y=mean, fill=SEX), stat = "identity" ,width=0.8,alpha=0.7, position=position_dodge(width=.9))+
  geom_errorbar(aes(x=scenario, ymin=mean-ci, ymax=mean+ci, group=SEX), width=0.2, colour="orange", alpha=0.9, position=position_dodge(width=1))+
  geom_text(aes(x=scenario, y=mean, group=SEX ,label=sprintf("%0.2f",round(mean, digits = 2))), 
            vjust=1.6, position = position_dodge(0.9),
            color="white", size=3.5)+
  theme_classic()+
  theme(legend.position ="bottom",
        legend.title = element_blank())+
  ylab("Level of Non-Acceptance")+
  xlab(NULL)+
  scale_y_continuous(breaks = c(0,1,2,3,4,5), expand = expansion(mult=c(0,0)))+
  coord_cartesian(ylim = c(0, 5.5))+
  scale_x_discrete(labels = c("brown_male_0" = "Non-White\nMale 0%", "brown_male_50" = "Non-White\nMale 50%",
                              "brown_male_100" = "Non-White\nMale 100%", "white_male_100" = "White\nMale 100%",
                              "German_male_0" = "German\nMale 0%", "German_male_50" = "German\nMale 50%",
                              "German_male_100" = "German\nMale 100%"))+
  scale_fill_manual(values = c("#4D4D4D","#CCCCCC"))

```

```{r}

# ggsave(filename = "U:/sex_ratio/output/Figure_S12.tiff", plot_non_accept_sex, width = 16, height = 10, dpi=300, units = "cm")

```


```{r, fig.height=6, fig.width=8}

# plot_non_accept_sex <-plot_non_accept_sex + stat_pvalue_manual(non_accept_sex_t_test, 
#                                                               label = "signif_weighted",y.position = c(5, 5.6, 6.2, 5, 6.7, 5, 7.2,
#                                                                                                        5.3, 5.9, 6.5, 5.3, 7.0, 5.3, 7.4),
#                                                               bracket.shorten = 0.03)

# plot_non_accept_sex

```

### Perceived Threats
#### Job competition
##### Unweighted pairwise p value
```{r}

threat_job_sex_t_test <-dt_for_sm %>% group_by(SEX)%>%
  pairwise_t_test(threat_job~scenario, pool.sd = FALSE)%>% 
  mutate(significance = case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

threat_job_sex_t_test <- threat_job_sex_t_test %>% add_xy_position(x="scenario", dodge=0.9)
threat_job_sex_t_test <- threat_job_sex_t_test %>% 
  filter(xmin==1&xmax==2&SEX=="Male"|xmin==1&xmax==2&SEX=="Female"|xmin==2&xmax==3&SEX=="Male"|xmin==2&xmax==3&SEX=="Female"|
           xmin==1&xmax==3&SEX=="Male"|xmin==1&xmax==3&SEX=="Female"|xmin==3&xmax==4&SEX=="Male"|xmin==3&xmax==4&SEX=="Female"|
           xmin==1&xmax==5&SEX=="Male"|xmin==1&xmax==5&SEX=="Female"|xmin==2&xmax==6&SEX=="Male"|xmin==2&xmax==6&SEX=="Female"|
           xmin==3&xmax==7&SEX=="Male"|xmin==3&xmax==7&SEX=="Female")

```



###### Weighted p value, combined into unweighted dataframe

```{r}
# data split into  male and female

data_male <-dt_for_sm %>% filter(SEX=="Male")
data_female <-dt_for_sm %>% filter(SEX=="Female")


# Function of weighted t-test for a pair of scenarios
perform_weighted_t_test <- function(data, scenario1, scenario2, psweight) {
  filtered_data <- data %>%
    filter(scenario %in% c(scenario1, scenario2))
  survey_design <- svydesign(ids = ~1, weights = psweight, data = filtered_data)
  weighted_t_test_result <- svyttest(threat_job ~ scenario, design = survey_design)
  return(weighted_t_test_result$p.value)
}

# Paired scenarios
scenario_pairs <- list(
  c("brown_male_0", "brown_male_50"),
  c("brown_male_0", "brown_male_100"),
  c("brown_male_0", "German_male_0"),
  c("brown_male_50", "brown_male_100"),
  c("brown_male_50", "German_male_50"),
  c("brown_male_100", "white_male_100"),
  c("brown_male_100", "German_male_100")
)

# Perform weighted t-test for each pair of scenarios
p_weighted_male <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_male, pair[1], pair[2], ~psweight)
})

p_weighted_male<- as.data.frame(p_weighted_male)

p_weighted_female <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_female, pair[1], pair[2], ~psweight)
})

p_weighted_female<- as.data.frame(p_weighted_female)
colnames(p_weighted_male)= colnames(p_weighted_female)
p_weighted <- bind_rows(p_weighted_male, p_weighted_female)

colnames(p_weighted) <- "p_weighted"

# Combine results
threat_job_sex_t_test <- cbind(threat_job_sex_t_test, p_weighted)

# Remove objects
rm(scenario_pairs, p_weighted_male, p_weighted_female, p_weighted)


threat_job_sex_t_test <- threat_job_sex_t_test %>% 
  mutate(signif_weighted = case_when(
    p_weighted < 0.001 ~ "***",
    p_weighted < 0.01 ~ "**",
    p_weighted < 0.05 ~ "*",
    p_weighted < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

```



```{r}

# Recode the values based on the SEX variable
threat_job_sex_t_test$xmin <- ifelse(threat_job_sex_t_test$SEX == "Male", threat_job_sex_t_test$xmin - 0.25, threat_job_sex_t_test$xmin + 0.25)
threat_job_sex_t_test$xmax <- ifelse(threat_job_sex_t_test$SEX == "Male", threat_job_sex_t_test$xmax - 0.25, threat_job_sex_t_test$xmax + 0.25)

```


```{r}


plot_threat_job_sex <- Job_com_sex %>% 
  ggplot()+
  geom_bar(aes(x=scenario, y=mean, fill=SEX), stat = "identity" ,width=0.8,alpha=0.7, position=position_dodge(width=.9))+
  geom_errorbar(aes(x=scenario, ymin=mean-ci, ymax=mean+ci, group=SEX), width=0.2, colour="orange", alpha=0.9, position=position_dodge(width=1))+
  geom_text(aes(x=scenario, y=mean, group=SEX ,label=sprintf("%0.2f",round(mean, digits = 2))), 
            vjust=1.6, position = position_dodge(0.9),
            color="white", size=3.5)+
  theme_classic()+
  theme(legend.position ="bottom",
        legend.title = element_blank())+
  ylab("Level of Perceived Threats")+
  xlab(NULL)+
  ggtitle("Job competition")+
  scale_y_continuous(breaks = c(0,1,2,3,4,5), expand = expansion(mult=c(0,0)))+
  coord_cartesian(ylim = c(0, 5.5))+
  scale_x_discrete(labels = c("brown_male_0" = "Non-White\nMale 0%", "brown_male_50" = "Non-White\nMale 50%",
                              "brown_male_100" = "Non-White\nMale 100%", "white_male_100" = "White\nMale 100%",
                              "German_male_0" = "German\nMale 0%", "German_male_50" = "German\nMale 50%",
                              "German_male_100" = "German\nMale 100%"))+
  scale_fill_manual(values = c("#4D4D4D","#CCCCCC"))

```


```{r}

# ggsave(filename = "U:/sex_ratio/output/Figure_S13.1.tiff", plot_threat_job_sex, width = 16, height = 10, dpi=300, units = "cm")

```

```{r, fig.height=6, fig.width=8}

#plot_threat_job_sex <-plot_threat_job_sex + stat_pvalue_manual(threat_job_sex_t_test, 
#                                                               label = "signif_weighted",y.position = c(5, 5.6, 6.2, 5, 6.7, 5, 7.2,
#                                                                                                        5.3, 5.9, 6.5, 5.3, 7.0, 5.3, 7.4),
#                                                               bracket.shorten = 0.03)

# plot_threat_job_sex

```

#### Mate competition
##### Unweighted pairwise p value
```{r}

threat_mate_sex_t_test <-dt_for_sm %>% group_by(SEX)%>%
  pairwise_t_test(threat_mate~scenario, pool.sd = FALSE)%>% 
  mutate(significance = case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

threat_mate_sex_t_test <- threat_mate_sex_t_test %>% add_xy_position(x="scenario", dodge=0.9)
threat_mate_sex_t_test <- threat_mate_sex_t_test %>% 
  filter(xmin==1&xmax==2&SEX=="Male"|xmin==1&xmax==2&SEX=="Female"|xmin==2&xmax==3&SEX=="Male"|xmin==2&xmax==3&SEX=="Female"|
           xmin==1&xmax==3&SEX=="Male"|xmin==1&xmax==3&SEX=="Female"|xmin==3&xmax==4&SEX=="Male"|xmin==3&xmax==4&SEX=="Female"|
           xmin==1&xmax==5&SEX=="Male"|xmin==1&xmax==5&SEX=="Female"|xmin==2&xmax==6&SEX=="Male"|xmin==2&xmax==6&SEX=="Female"|
           xmin==3&xmax==7&SEX=="Male"|xmin==3&xmax==7&SEX=="Female")

```



###### Weighted p value, combined into unweighted dataframe

```{r}
# data split into  male and female

data_male <-dt_for_sm %>% filter(SEX=="Male")
data_female <-dt_for_sm %>% filter(SEX=="Female")


# Function of weighted t-test for a pair of scenarios
perform_weighted_t_test <- function(data, scenario1, scenario2, psweight) {
  filtered_data <- data %>%
    filter(scenario %in% c(scenario1, scenario2))
  survey_design <- svydesign(ids = ~1, weights = psweight, data = filtered_data)
  weighted_t_test_result <- svyttest(threat_mate ~ scenario, design = survey_design)
  return(weighted_t_test_result$p.value)
}

# Paired scenarios
scenario_pairs <- list(
  c("brown_male_0", "brown_male_50"),
  c("brown_male_0", "brown_male_100"),
  c("brown_male_0", "German_male_0"),
  c("brown_male_50", "brown_male_100"),
  c("brown_male_50", "German_male_50"),
  c("brown_male_100", "white_male_100"),
  c("brown_male_100", "German_male_100")
)

# Perform weighted t-test for each pair of scenarios
p_weighted_male <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_male, pair[1], pair[2], ~psweight)
})

p_weighted_male<- as.data.frame(p_weighted_male)

p_weighted_female <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_female, pair[1], pair[2], ~psweight)
})

p_weighted_female<- as.data.frame(p_weighted_female)
colnames(p_weighted_male)= colnames(p_weighted_female)
p_weighted <- bind_rows(p_weighted_male, p_weighted_female)

colnames(p_weighted) <- "p_weighted"

# Combine results
threat_mate_sex_t_test <- cbind(threat_mate_sex_t_test, p_weighted)

# Remove objects
rm(scenario_pairs, p_weighted_male, p_weighted_female, p_weighted)


threat_mate_sex_t_test <- threat_mate_sex_t_test %>% 
  mutate(signif_weighted = case_when(
    p_weighted < 0.001 ~ "***",
    p_weighted < 0.01 ~ "**",
    p_weighted < 0.05 ~ "*",
    p_weighted < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

```


```{r}

# Recode the values based on the SEX variable
threat_mate_sex_t_test$xmin <- ifelse(threat_mate_sex_t_test$SEX == "Male", threat_mate_sex_t_test$xmin - 0.25, threat_mate_sex_t_test$xmin + 0.25)
threat_mate_sex_t_test$xmax <- ifelse(threat_mate_sex_t_test$SEX == "Male", threat_mate_sex_t_test$xmax - 0.25, threat_mate_sex_t_test$xmax + 0.25)

```


```{r}


plot_threat_mate_sex <- Mate_com_sex  %>% 
  ggplot()+
  geom_bar(aes(x=scenario, y=mean, fill=SEX), stat = "identity" ,width=0.8,alpha=0.7, position=position_dodge(width=.9))+
  geom_errorbar(aes(x=scenario, ymin=mean-ci, ymax=mean+ci, group=SEX), width=0.2, colour="orange", alpha=0.9, position=position_dodge(width=1))+
  geom_text(aes(x=scenario, y=mean, group=SEX ,label=sprintf("%0.2f",round(mean, digits = 2))), 
            vjust=1.6, position = position_dodge(0.9),
            color="white", size=3.5)+
  theme_classic()+
  theme(legend.position ="bottom",
        legend.title = element_blank())+
  ylab("Level of Perceived Threats")+
  xlab(NULL)+
  ggtitle("Mate competition")+
  scale_y_continuous(breaks = c(0,1,2,3,4,5), expand = expansion(mult=c(0,0)))+
  coord_cartesian(ylim = c(0,5.5))+
  scale_x_discrete(labels = c("brown_male_0" = "Non-White\nMale 0%", "brown_male_50" = "Non-White\nMale 50%",
                              "brown_male_100" = "Non-White\nMale 100%", "white_male_100" = "White\nMale 100%",
                              "German_male_0" = "German\nMale 0%", "German_male_50" = "German\nMale 50%",
                              "German_male_100" = "German\nMale 100%"))+
  scale_fill_manual(values = c("#4D4D4D","#CCCCCC"))

```

```{r}

 ggsave(filename = "U:/sex_ratio/output/Figure_S13.2.tiff", plot_threat_mate_sex, width = 16, height = 10, dpi=300, units = "cm")

```

```{r, fig.height=6, fig.width=8}

#plot_threat_mate_sex <-plot_threat_mate_sex + stat_pvalue_manual(threat_mate_sex_t_test, 
#                                                               label = "signif_weighted",y.position = c(5, 5.6, 6.2, 5, 6.7, 5, 7.2,
#                                                                                                        5.3, 5.9, 6.5, 5.3, 7.0, 5.3, 7.4),
#                                                               bracket.shorten = 0.03)

# plot_threat_mate_sex

```

#### Safety
##### Unweighted pairwise p value
```{r}

threat_safe_sex_t_test <-dt_for_sm %>% group_by(SEX)%>%
  pairwise_t_test(threat_safety~scenario, pool.sd = FALSE)%>% 
  mutate(significance = case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    p < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

threat_safe_sex_t_test <- threat_safe_sex_t_test %>% add_xy_position(x="scenario", dodge=0.9)
threat_safe_sex_t_test <- threat_safe_sex_t_test %>% 
  filter(xmin==1&xmax==2&SEX=="Male"|xmin==1&xmax==2&SEX=="Female"|xmin==2&xmax==3&SEX=="Male"|xmin==2&xmax==3&SEX=="Female"|
           xmin==1&xmax==3&SEX=="Male"|xmin==1&xmax==3&SEX=="Female"|xmin==3&xmax==4&SEX=="Male"|xmin==3&xmax==4&SEX=="Female"|
           xmin==1&xmax==5&SEX=="Male"|xmin==1&xmax==5&SEX=="Female"|xmin==2&xmax==6&SEX=="Male"|xmin==2&xmax==6&SEX=="Female"|
           xmin==3&xmax==7&SEX=="Male"|xmin==3&xmax==7&SEX=="Female")

```



###### Weighted p value, combined into unweighted dataframe

```{r}
# data split into  male and female

data_male <-dt_for_sm %>% filter(SEX=="Male")
data_female <-dt_for_sm %>% filter(SEX=="Female")


# Function of weighted t-test for a pair of scenarios
perform_weighted_t_test <- function(data, scenario1, scenario2, psweight) {
  filtered_data <- data %>%
    filter(scenario %in% c(scenario1, scenario2))
  survey_design <- svydesign(ids = ~1, weights = psweight, data = filtered_data)
  weighted_t_test_result <- svyttest(threat_safety ~ scenario, design = survey_design)
  return(weighted_t_test_result$p.value)
}

# Paired scenarios
scenario_pairs <- list(
  c("brown_male_0", "brown_male_50"),
  c("brown_male_0", "brown_male_100"),
  c("brown_male_0", "German_male_0"),
  c("brown_male_50", "brown_male_100"),
  c("brown_male_50", "German_male_50"),
  c("brown_male_100", "white_male_100"),
  c("brown_male_100", "German_male_100")
)

# Perform weighted t-test for each pair of scenarios
p_weighted_male <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_male, pair[1], pair[2], ~psweight)
})

p_weighted_male<- as.data.frame(p_weighted_male)

p_weighted_female <- sapply(scenario_pairs, function(pair) {
  perform_weighted_t_test(data_female, pair[1], pair[2], ~psweight)
})

p_weighted_female<- as.data.frame(p_weighted_female)
colnames(p_weighted_male)= colnames(p_weighted_female)
p_weighted <- bind_rows(p_weighted_male, p_weighted_female)

colnames(p_weighted) <- "p_weighted"

# Combine results
threat_safe_sex_t_test <- cbind(threat_safe_sex_t_test, p_weighted)

# Remove objects
rm(scenario_pairs, p_weighted_male, p_weighted_female, p_weighted)


threat_safe_sex_t_test <- threat_safe_sex_t_test %>% 
  mutate(signif_weighted = case_when(
    p_weighted < 0.001 ~ "***",
    p_weighted < 0.01 ~ "**",
    p_weighted < 0.05 ~ "*",
    p_weighted < 0.1 ~ ".",
    TRUE ~ "ns"
  )) 

```



```{r}

# Recode the values based on the SEX variable
threat_safe_sex_t_test$xmin <- ifelse(threat_safe_sex_t_test$SEX == "Male", threat_safe_sex_t_test$xmin - 0.25, threat_safe_sex_t_test$xmin + 0.25)
threat_safe_sex_t_test$xmax <- ifelse(threat_safe_sex_t_test$SEX == "Male", threat_safe_sex_t_test$xmax - 0.25, threat_safe_sex_t_test$xmax + 0.25)

```


```{r}


plot_threat_safe_sex <- Safe_con_sex  %>% 
  ggplot()+
  geom_bar(aes(x=scenario, y=mean, fill=SEX), stat = "identity" ,width=0.8,alpha=0.7, position=position_dodge(width=.9))+
  geom_errorbar(aes(x=scenario, ymin=mean-ci, ymax=mean+ci, group=SEX), width=0.2, colour="orange", alpha=0.9, position=position_dodge(width=1))+
  geom_text(aes(x=scenario, y=mean, group=SEX ,label=sprintf("%0.2f",round(mean, digits = 2))), 
            vjust=1.6, position = position_dodge(0.9),
            color="white", size=3.5)+
  theme_classic()+
  theme(legend.position ="bottom",
        legend.title = element_blank())+
  ylab("Level of Perceived Threats")+
  xlab(NULL)+
  ggtitle("Safety")+
  scale_y_continuous(breaks = c(0,1,2,3,4,5), expand = expansion(mult=c(0,0)))+
  coord_cartesian(ylim = c(0,5.5))+
  scale_x_discrete(labels = c("brown_male_0" = "Non-White\nMale 0%", "brown_male_50" = "Non-White\nMale 50%",
                              "brown_male_100" = "Non-White\nMale 100%", "white_male_100" = "White\nMale 100%",
                              "German_male_0" = "German\nMale 0%", "German_male_50" = "German\nMale 50%",
                              "German_male_100" = "German\nMale 100%"))+
  scale_fill_manual(values = c("#4D4D4D","#CCCCCC"))

plot_threat_safe_sex

```

```{r}

# ggsave(filename = "U:/sex_ratio/output/Figure_S13.3.tiff", plot_threat_safe_sex, width = 16, height = 10, dpi=300, units = "cm")

```

```{r, fig.height=6, fig.width=8}

# plot_threat_safe_sex <-plot_threat_safe_sex + stat_pvalue_manual(threat_safe_sex_t_test, 
#                                                               label = "signif_weighted",y.position = c(5, 5.6, 6.2, 5, 6.7, 5, 7.2,
#                                                                                                        5.3, 5.9, 6.5, 5.3, 7.0, 5.3, 7.4),
#                                                               bracket.shorten = 0.03)

# plot_threat_safe_sex

```

> Threats to German culture is not asked to German influx groups, Figure 4 in the main text has shown the all groups








